flowers-pilot-analysis

### 2021-08-19 code/aa-flowers-pilot_analysis.Rmd
add collaborative and competitive first round game data

# Pre-process
Remove joined_data and uncomment the following block to rerun the preprocessing scripts
```{r process-data, message=FALSE, warning=FALSE}
data_list <- c("pilots")
process_all_data(data_list)
join_all_data()
```

@@

Game counts
```{r}
#pull out pilots
d.games %>% group_by(conditionName, chatEnabled,pilot)%>% tally()
```

@@

### Time
```{r, fig.height=5, fig.width=3}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = gameLength/60, 
             color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ 
  labs(y = "Time (In Minutes)", title = "Game Length", x = "Language Condition")+
  ylim(0, 90)+
  scale_color_bay() + theme_jmank() +  theme(legend.position = "none")
ggsave(here(fig_path, "time_distirbution.png"),  width = 3, height = 5)

@@

### Number of Words
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = gameNumWords, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ labs(y = "N. Words", title = "Number of Words Exchanged", x = "Language Condition")+scale_color_bay() + theme_jmank() +  theme(legend.position = "none")

@@

```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = log(gameNumWords+1), color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ labs(y = "Log N. Words Exchanged")+
  scale_color_bay() + theme_jmank() +  theme(legend.position = "none")
ggsave(here(fig_path, "numwords_log_distirbution.png"))

@@

```{r}
ms <- d.by_game_metrics %>%
  mutate(langUse = ifelse(gameNumWords > 0, TRUE, FALSE)) %>% 
  group_by(condition, langUse) %>%
  summarise(mean_nw = mean(gameNumWords),
            ci_nw = 1.96 * sd(gameNumWords) / sqrt(length(gameLength)),
            mean_points = mean(gamePoints),
            ci_points = 1.96 * sd(gamePoints) / sqrt(length(gameLength)))

d.by_game_metrics %>%
  mutate(langUse = ifelse(gameNumWords > 0, TRUE, FALSE)) %>% 
  ggplot(aes(x = gameNumWords, y = gamePoints, color = condition, shape = langUse)) +
  #geom_smooth(aes(group = condition), method = "lm") +
  geom_point(alpha = .5) +
  geom_pointrange(data = ms, aes(x = mean_nw, y = mean_points, 
                                 ymin = mean_points - ci_points,
                                 ymax = mean_points + ci_points)) +
  geom_errorbarh(data = ms, aes(x = mean_nw, y = mean_points, 
                                 xmin = mean_nw - ci_nw,
                                 xmax = mean_nw + ci_nw), width = 0) + 
  # ylim(0,1500) + 
  labs(x = "Words Echanged", y = "Points Earned") + 
  scale_color_bay() + theme_jmank() +  
  theme(legend.position = "bottom")
```

@@

Are they getting better over games?
```{r}
d.by_round_metrics %>% left_join(d.games %>% 
                                   select(gameId, condition, chatEnabled))%>%
  mutate(blockName = paste0("Block ", blockNum))%>% 
  ggplot(aes(x = log(groupNumWords+1), y = roundPointsAdjusted, 
             color = condition)) + 
  geom_point(alpha = .25) + theme_jmank() + scale_color_bay() + facet_wrap(~blockName) +
  labs(title = "Number of points per trial")
```

>>>>

# Pre-process
Remove joined_data and uncomment the following block to rerun the preprocessing scripts
```{r process-data, message=FALSE, warning=FALSE}
data_list <- c("pilots", "collab_lang_20", "compet_lang_20")
process_all_data(data_list)
#join_all_data()
```

@@

Game counts
```{r}
#pull out pilots
game_completion %>% group_by(condition, chat, gameComplete)%>% tally()
```

@@

### Time
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = condition, y = gameLength/60, 
             color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  #facet_grid(cols = vars(condition))+ 
  labs(y = "Time (In Minutes)", title = "Game Length", x = "Condition")+
  scale_color_bay() + theme_jmank() +  theme(legend.position = "none")
ggsave(here(fig_path, "time_distirbution.png"),  width = 5, height = 3)

@@

### Number of Words
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = condition, y = gameNumWords, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  #facet_grid(cols = vars(condition))+ 
  labs(y = "N. Words", title = "Number of Words Exchanged", x = "Condition")+scale_color_bay() + theme_jmank() +  theme(legend.position = "none")

@@

```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = condition, y = log(gameNumWords+1), color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  #facet_grid(cols = vars(condition))+ 
  labs(y = "Log N. Words Exchanged")+
  scale_color_bay() + theme_jmank() +  theme(legend.position = "none")
ggsave(here(fig_path, "numwords_log_distirbution.png"))

@@

```{r, fig.width=5, fig.height=3}
ms <- d.by_game_metrics %>%
  mutate(langUse = ifelse(gameNumWords > 0, TRUE, FALSE)) %>% 
  group_by(condition) %>%
  summarise(mean_nw = mean(gameNumWords),
            ci_nw = 1.96 * sd(gameNumWords) / sqrt(length(gameLength)),
            mean_points = mean(gamePoints),
            ci_points = 1.96 * sd(gamePoints) / sqrt(length(gameLength)))

d.by_game_metrics %>%
  mutate(langUse = ifelse(gameNumWords > 0, TRUE, FALSE)) %>% 
  ggplot(aes(x = gameNumWords, y = gamePoints, color = condition)) +
  #geom_smooth(aes(group = condition), method = "lm") +
  geom_point(alpha = .5) +
  geom_pointrange(data = ms, aes(x = mean_nw, y = mean_points, 
                                 ymin = mean_points - ci_points,
                                 ymax = mean_points + ci_points)) +
  geom_errorbarh(data = ms, aes(x = mean_nw, y = mean_points, 
                                 xmin = mean_nw - ci_nw,
                                 xmax = mean_nw + ci_nw), width = 0) + 
  # ylim(0,1500) + 
  labs(x = "Words Exchanged (Game)", y = "Points Earned (Game)") + 
  scale_color_bay() + theme_jmank() +  
  theme(legend.position = "bottom")
```

@@

Are they getting better over games?
```{r}
d.by_round_metrics %>% left_join(d.games %>% 
                                   select(gameId, condition, chatEnabled))%>%
  mutate(blockName = paste0("Block ", blockNum))%>% 
  ggplot(aes(x = groupNumWords, y = roundPointsAdjusted, 
             color = condition)) + 
  geom_point(alpha = .25) + theme_jmank() + scale_color_bay() + facet_wrap(~blockName) +
  labs(title = "Number of points per trial")
```
